### 2016-03-30 Chapters/paper2.tex
Correctly added some cites and bibliography

When the problem is discretized, this maximum property may be inherited by what is called \textit{discrete maximum principle} (DMP). Several definitions of the DMP have been proposed in the literature for continuous discrete approximations (see \cite{codina_discontinuity-capturing_1993,hohn_remarks_1981,varga_discrete_1966,burman_edge_2004,roos2008robust}). Some of them are equivalent while some others are weaker or stronger. There is also a lot of literature about the conditions on the mesh for the Poisson problem to enjoy the DMP \cite{hohn_remarks_1981,vejchodsky_discrete_2007,horvath_discrete_2013,payette_performance_2012} as well as discrete methods specially implemented to fulfil such property. Methods have been designed for linear finite differences \cite{ciarlet_discrete_1970} and continuous linear finite elements \cite{ciarlet_maximum_1973,codina_discontinuity-capturing_1993,mizukami_petrov-galerkin_1985,burman_discrete_2004,burman_edge_2004,burman2005stabilized}. {These methods are implicit in sense, and usually based on the addition of AV to the problem at hand; they are traditionally called shock (or discontinuity)-capturing techniques, even though we favour the notation \emph{nonlinear stabilization}.} 
%There is also a interesting simple approach to the problem given by Kreuzer \cite{kreuzer_note_2012} consisting on applying a simple cutoff to the solution but it can not be applied in an implicit code and moreover it only works when the maximum and the minimum of the problem are known beforehand. 
Some approaches to prove a DMP using piecewise higher order polynomials have been done \cite{nagarajan_enforcing_2011,payette_performance_2012,kuzmin_design_2008,vejchodsky_discrete_2007,vejchodsky_higher-order_2010,yanik_discrete_1987,yanik_sufficient_1989} but only the Poisson problem has been proved to enjoy the DMP and only on certain one-dimensional (1D) meshes \cite{vejchodsky_discrete_2007} and on very restrictive quadratic and cubic two dimensional meshes \cite{lorenz_zur_1977,hohn_remarks_1981}. When it comes to discontinuous methods, most of the shock capturing techniques are based on the concept of slope limiter, proposed by Cockburn and Shu for conservation laws \cite{cockburn_rungekutta_1998,cockburn_runge-kutta_1990} and latter adapted to the convection-dominated convection-diffusion problem  \cite{cockburn_rungekutta_2001}. The same strategy can be applied to finite volume methods (see \cite{zhang_maximum-principle-satisfying_2010,zhang_maximum-principle-satisfying_2011,zhang_maximum-principle-satisfying_2012}). Again, these methods consist in a postprocess after the solution is computed and are designed for explicit methods. {However, as far as we know, there are no works dealing with nonlinear stabilization and implicit DMP-preserving dG formulations. In fact, even the definition of what a DMP for dG means is open.}

@@

Now we are ready to design the AV in order to obtain a dG formulation satisfying the DMP property defined above. In particular, we will consider a piecewise constant AV function $\varepsilon_h=\varepsilon_h(u_h)$ such that, when added to $\mu_h$, takes values in a bounded interval $\mu_K + \varepsilon_K := \mu_h|_K + \varepsilon_h|_K\in [0,\Lambda_K]$, where $\Lambda_K=\max\{\nu \|\beta\|_\infty h_{K},\mu_K\}$ is the maximum amount of viscosity admitted in an element and $\nu>0$ is a parameter to be fixed. We want that, if $u_h$ has a local discrete extremum on $x_i$ in $K$, then  $\mu_{K}+ \varepsilon_{K} = \Lambda_{K}$. This will be achieved by scaling the AV using a shock detector $s(u_h)$ that will take values in the interval $[0,1]$ with $s=1$ in $K$ if there is a local discrete extremum in the element. { Notice that if $\mu_K+\varepsilon_K = \Lambda_K$ in every element $K$, the AV would correspond to the suboptimal isotropic diffusion introduced by Von Neumann and Richtmyer in \cite{vonneumann1950method} for the continuous case}. We will start by designing the detector $s$ for $1$D and then we will extend the definition to the multidimensional case.

>>>>

When the problem is discretized, this maximum property may be inherited by what is called \textit{discrete maximum principle} (DMP). Several definitions of the DMP have been proposed in the literature for continuous discrete approximations (see \cite{codina_discontinuity-capturing_1993,hohn_remarks_1981,varga_discrete_1966,burman_edge_2004,roos_robust_2008}). Some of them are equivalent while some others are weaker or stronger. There is also a lot of literature about the conditions on the mesh for the Poisson problem to enjoy the DMP \cite{hohn_remarks_1981,vejchodsky_discrete_2007,horvath_discrete_2013,payette_performance_2012} as well as discrete methods specially implemented to fulfil such property. Methods have been designed for linear finite differences \cite{ciarlet_discrete_1970} and continuous linear finite elements \cite{ciarlet_maximum_1973,codina_discontinuity-capturing_1993,mizukami_petrov-galerkin_1985,burman_discrete_2004,burman_edge_2004,burman_stabilized_2005}. {These methods are implicit in sense, and usually based on the addition of AV to the problem at hand; they are traditionally called shock (or discontinuity)-capturing techniques, even though we favour the notation \emph{nonlinear stabilization}.} 
%There is also a interesting simple approach to the problem given by Kreuzer \cite{kreuzer_note_2012} consisting on applying a simple cutoff to the solution but it can not be applied in an implicit code and moreover it only works when the maximum and the minimum of the problem are known beforehand. 
Some approaches to prove a DMP using piecewise higher order polynomials have been done \cite{nagarajan_enforcing_2011,payette_performance_2012,kuzmin_design_2008,vejchodsky_discrete_2007,vejchodsky_higher-order_2010,yanik_discrete_1987,yanik_sufficient_1989} but only the Poisson problem has been proved to enjoy the DMP and only on certain one-dimensional (1D) meshes \cite{vejchodsky_discrete_2007} and on very restrictive quadratic and cubic two dimensional meshes \cite{lorenz_zur_1977,hohn_remarks_1981}. When it comes to discontinuous methods, most of the shock capturing techniques are based on the concept of slope limiter, proposed by Cockburn and Shu for conservation laws \cite{cockburn_rungekutta_1998,cockburn_runge-kutta_1990} and latter adapted to the convection-dominated convection-diffusion problem  \cite{cockburn_rungekutta_2001}. The same strategy can be applied to finite volume methods (see \cite{zhang_maximum-principle-satisfying_2010,zhang_maximum-principle-satisfying_2011,zhang_maximum-principle-satisfying_2012}). Again, these methods consist in a postprocess after the solution is computed and are designed for explicit methods. {However, as far as we know, there are no works dealing with nonlinear stabilization and implicit DMP-preserving dG formulations. In fact, even the definition of what a DMP for dG means is open.}

@@

Now we are ready to design the AV in order to obtain a dG formulation satisfying the DMP property defined above. In particular, we will consider a piecewise constant AV function $\varepsilon_h=\varepsilon_h(u_h)$ such that, when added to $\mu_h$, takes values in a bounded interval $\mu_K + \varepsilon_K := \mu_h|_K + \varepsilon_h|_K\in [0,\Lambda_K]$, where $\Lambda_K=\max\{\nu \|\beta\|_\infty h_{K},\mu_K\}$ is the maximum amount of viscosity admitted in an element and $\nu>0$ is a parameter to be fixed. We want that, if $u_h$ has a local discrete extremum on $x_i$ in $K$, then  $\mu_{K}+ \varepsilon_{K} = \Lambda_{K}$. This will be achieved by scaling the AV using a shock detector $s(u_h)$ that will take values in the interval $[0,1]$ with $s=1$ in $K$ if there is a local discrete extremum in the element. { Notice that if $\mu_K+\varepsilon_K = \Lambda_K$ in every element $K$, the AV would correspond to the suboptimal isotropic diffusion introduced by Von Neumann and Richtmyer in \cite{von_neumann_method_1950} for the continuous case}. We will start by designing the detector $s$ for $1$D and then we will extend the definition to the multidimensional case.
